### 2021-12-19 README.Rmd
UPDATE README

<!-- badges: start -->
[![Launch Rstudio Binder](http://mybinder.org/badge_logo.svg)](https://mybinder.org/v2/gh/jmlondon/berchukHaulout/main?urlpath=rstudio)
[![DOI](https://zenodo.org/badge/DOI/10.5281/zenodo.4638221.svg)](https://doi.org/10.5281/zenodo.4638221)
<!-- badges: end -->

## Haul-out behavior and aerial survey detectability of seals in the Bering and Chukchi seas
Josh M. London^1^,✉, Paul B. Conn^1^, Stacie K. Hardy^1^, Erin L. Richmond^1^, Jay M. Ver Hoef^1^, Irina S. Trukhanova^1^, Michael F. Cameron^1^, and Peter L. Boveng^1^
1 Marine Mammal Laboratory, Alaska Fisheries Science Center, NOAA Fisheries, Seattle, Washington, USA
✉ Correspondence: Josh M. London <josh.london@noaa.gov>

@@

  - [:file\_folder: paper](/analysis/paper): R Markdown source document
    for manuscript. Includes code to reproduce the figures and tables
    generated by the analysis. It also has a rendered version,
    `paper.docx`, suitable for reading (the code is replaced by figures
    and tables in this file)
  - [:file\_folder: figures](/analysis/figures): figures generated
  - [:file\_folder: scripts](/analysis/scripts): R scripts in support of analysis.
  - [:file\_folder: templates](/analysis/templates): template files and scripts.

@@

  - [:file\_folder: data](/data): Data used or generated in analysis

## How to run in your broswer or download and run locally

This research compendium has been developed using the statistical programming
language R. To work with the compendium, you will need
installed on your computer the [R software](https://cloud.r-project.org/)
itself and optionally [RStudio Desktop](https://rstudio.com/products/rstudio/download/).

The simplest way to explore the text, code and data is to click on
[binder](https://mybinder.org/v2/gh/jmlondon/berchukHaulout/main?urlpath=rstudio)
to open an instance of RStudio in your browser, which will have the
compendium files ready to work with. Binder uses rocker-project.org
Docker images to ensure a consistent and reproducible computational
environment. These Docker images can also be used locally.

>>>>

<!-- badges: start -->
[![DOI](https://zenodo.org/badge/DOI/10.5281/zenodo.4638221.svg)](https://doi.org/10.5281/zenodo.4638221)
<!-- badges: end -->

## Haul-out behavior and aerial survey detectability of seals in the Bering and Chukchi seas
Josh M. London^1^,✉, Paul B. Conn^1^, Stacie K. Hardy^1^, Erin L. Richmond^1^, Jay M. Ver Hoef^1^, Michael F. Cameron^1^, Justin Crawford^2^, Andrew L. Von Duyke^3^, Lori T. Quakenbush^2^, and Peter L. Boveng^1^

1. Marine Mammal Laboratory, Alaska Fisheries Science Center, NOAA Fisheries, Seattle, Washington, USA
2. Arctic Marine Mammals Program, Alaska Department of Fish and Game, Fairbanks, Alaska, USA
3. Department of Wildlife Management, North Slope Borough, Utqiaġvik, Alaska, USA

✉ Correspondence: Josh M. London <josh.london@noaa.gov>

@@

  - [:file\_folder: paper](/analysis/paper): R Markdown source document
    for manuscript. Includes code to reproduce the figures and tables
    generated by the analysis. It also has a rendered version,
    `London_HauloutBehavior.docx`, suitable for reading (the code is replaced by figures
    and tables in this file)
  - [:file\_folder: figures](/analysis/figures): figures generated
  - [:file\_folder: scripts](/analysis/scripts): R scripts in support of analysis.
  - [:file\_folder: templates](/analysis/templates): template files and scripts.

@@

  - [:file\_folder: data](/data): data used for model fits and final model output

### {targets} and {renv} packages

This repository relies heavily on the {targets} and {renv} packages for management
of analysis pipelines and reproducibility.

  - [:file\_folder: R](/R): pipeline functions developed in support or target pipeline
  - [:page\_facing\_up: _targets.R](/_targets.R): target pipeline
  - [:page\_facing\_up: renv.lock](/renv.lock): renv lockfile
